---
title: "main-functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{main-functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(plasticGeo)
```

```{r}
#| eval: false
top_plastic_items(neighborhood = "Agege", n = 3)
```

### This function will take in a neighborhood in the Nigeria dataset (Agege, Amuwo Odofin, Apapa, Eti Osa, Ibeju Lekki, Port-Harcourt, Surulere) we have data on and output the top 3 plastic items and counts for each type of plastic item. 

```{r}
#| eval: false
plot_temp_plastic_hex()
```
### This function should create a hexbin plot comparing mean annual temperature and total plastic collected. It should find the country with the highest total plastic collected, highlight that point, and label it with the country name. It will also include a linear trend line and a fill scale showing the number of countries in each hexbin.


```{r}
#| eval: false
top_plastic_cards(item_cols = c(plastic_bottles, bottle_caps, wrappers_labels), n_items = 3,
title = "Counts for the Top 3 Plastic Items Found in Lagos & Rivers Beach Cleanups"
)
```
### This function would shorten the dashboard code by adding up the plastic item columns, ranking the items by total count, and displaying the top 3 as value boxes. We could call one function and reuse it for different locations, years, or plastic item groups.
